Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-14 concurrency/CONCUR 2023/paper.tex
re-structured paper

\section{Search Structure Templates in VST}
The C implementation of a node in our template style is:
\begin{lstlisting}[language = C, backgroundcolor=\color{white}, basicstyle=\ttfamily\footnotesize]
typedef struct node_t {node *t; lock_t *lock;} node_t;
\end{lstlisting}
\than{I changed \lstinline{tree_t} into \lstinline{node_t}, and \lstinline{tree} into \lstinline{node}, since concurrent search structure will not depend on particular data structures.}

@@

\subsection{Lock-coupling Template}
The lock-coupling template employs the hand-over-hand locking scheme to prevent interference from other threads during traversal. Each thread continuously maintains at least one lock during traversal between nodes, ensuring that other threads cannot interfere with the traversal or invalidate the ongoing search.

@@

\begin{figure}[ht]
	\begin{subfigure}[t]{0.45\textwidth}
		\lstinputlisting[language=caml, style=myStyle]{lock_traverse.ml} 
		\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in an ML-like language \cite{krishna2019compositional} \wm{Shouldn't it be lock and then unlock?}}
		\than{I copied exactly the same from thesis of Krishna. However, in the their of proofs, they had lock before unlock like you said. Do we need to changed to fit with our context and their code?} 
		\label{traverse_lock_a}	
	\end{subfigure}\qquad
	\begin{subfigure}[t]{0.48\textwidth}
		\lstinputlisting[language=C, style=myStyle]{lock_traverse.c} 
		\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in C}
		\label{traverse_lock_b}
	\end{subfigure}
	\caption{The \lstinline{traverse} method of the lock-coupling template algorithms}
	\label{traverse_lock}
\end{figure}

@@

\subsection{Give-Up}
The give-up template is an algorithm for implementing concurrent search in a tree data structure. Unlike the lock-coupling template, which maintains locks during traversal between nodes, the give-up template takes an \emph{optimistic concurrency control} approach \lb{c.f. RCU}, only acquiring locks when loading or storing to a node. This reduces the amount of time that locks are held and makes the algorithm more scalable in highly-contended scenarios. Each node has a range field that serves as a reference point for threads to determine if they are still on the correct path. If a thread finds that it has deviated from the expected path, it abandons the node by releasing the lock and returns to the root node to start again. This behavior aligns with the give-up template algorithm's approach, in which threads terminate their search upon encountering obstacles or deviating from the expected path.

@@

@@

\subsection{Lock-coupling Template}
Proceeding with the proofs, we establish the following specification for the \lstinline{traverse} function in the lock-coupling template:

@@

\subsection{Give-up Template}
Moving forward with the proofs, we define the following specification for the traverse function within the give-up template:

>>>>

\section{Search Structure Templates in VST}

\subsection{Search Structure Templates}
The C implementation of a node in our template style is:
\begin{lstlisting}[language = C, backgroundcolor=\color{white}, basicstyle=\ttfamily\footnotesize]
typedef struct node_t {node *t; lock_t *lock;} node_t;
\end{lstlisting}
\than{I changed \lstinline{tree_t} into \lstinline{node_t}, and \lstinline{tree} into \lstinline{node}, since concurrent search structure will not depend on particular data structures.}

@@

\subsubsection{Lock-coupling Template}
The lock-coupling template employs the hand-over-hand locking scheme to prevent interference from other threads during traversal. Each thread continuously maintains at least one lock during traversal between nodes, ensuring that other threads cannot interfere with the traversal or invalidate the ongoing search.

@@

\begin{figure}[ht]
	\begin{subfigure}[t]{0.45\textwidth}
		\lstinputlisting[language=caml, style=myStyle]{lock_traverse.ml} 
		\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in an ML-like language \cite{krishna2019compositional}} 
			%\wm{Shouldn't it be lock and then unlock?}} \than{I copied exactly the same from thesis of Krishna. However, in the their of proofs, they had lock before unlock like you said. Do we need to changed to fit with our context and their code?} 
		\label{traverse_lock_a}	
	\end{subfigure}\qquad
	\begin{subfigure}[t]{0.48\textwidth}
		\lstinputlisting[language=C, style=myStyle]{lock_traverse.c} 
		\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in C}
		\label{traverse_lock_b}
	\end{subfigure}
	\caption{The \lstinline{traverse} method of the lock-coupling template algorithms}
	\label{traverse_lock}
\end{figure}

@@

\subsubsection{Give-Up Template}
The give-up template is an algorithm for implementing concurrent search in a tree data structure. Unlike the lock-coupling template, which maintains locks during traversal between nodes, the give-up template takes an \emph{optimistic concurrency control} approach \lb{c.f. RCU}, only acquiring locks when loading or storing to a node. This reduces the amount of time that locks are held and makes the algorithm more scalable in highly-contended scenarios. Each node has a range field that serves as a reference point for threads to determine if they are still on the correct path. If a thread finds that it has deviated from the expected path, it abandons the node by releasing the lock and returns to the root node to start again. This behavior aligns with the give-up template algorithm's approach, in which threads terminate their search upon encountering obstacles or deviating from the expected path.

@@

\subsection{Proofs of Templates} \than{Can someone suggest another title?}

@@

\subsubsection{Lock-coupling Template}
Proceeding with the proofs, we establish the following specification for the \lstinline{traverse} function in the lock-coupling template:

@@

\subsubsection{Give-up Template}
Moving forward with the proofs, we define the following specification for the traverse function within the give-up template:
